Autogenerated Questions Paper Draft

### 2018-04-09 paper_draft/paper_draft.tex
Add to formatting

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily}

\usepackage{fancyvrb}

@@

\begin{Verbatim}[tabsize=4]
::Dynamic Expressions Level 1 #005::
Solve the following problem: 
<pre> int item = 4; 
int bar = item / 3 - 3;</pre>
What is the variable "bar" equal to?
	{ 
	=-2 
	~-0.5 
	~-1.667 
	~1.5 
	~0 
	}
\end{Verbatim}

@@

NOTE: Before we talk about unique answer guarantee, we should talk about distractors: what they are, why they are important, how others use them/disregard them/why they should be convincing. Also we should provide some concrete examples.

@@

Because of the universal format for questions, extra error checks can be done across all categories. While there is no general way
to ensure that each question provides the correct answer, we can confirm that each answer is unique
(and especially that no distractor is the same as the right answer) -- a seemingly trivial, but essential, restraint.
This can become complicated is for two reasons: i) in an effort to create more convincing distractors,
each difficulty in each category generates its own distractors using "clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes) and ii) complex answers
(in particular, answers containing vectors; see Arrays) become more difficult to compare and even more difficult
to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
In the case of (i), it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of (ii), if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see Arrays
Difficulty 1). It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

@@

NOTE: Maybe here is a quick section where we talk about preventing trivial cases. Each category looks for cases like (x - x), and x / 1, etc. Also should we talk about trivial distractors -- similar to how the unique answer guarantee basically falls on trivial answers as a last resort.

@@

\begin{lstlisting}[language=C++]
int documents = 8;
int bar = 10;
(bar < = documents) != (10 < 9)
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}

@@

%\begin{Verbatim}
%What is the value of "bar" after the switch case block?
%\end{Verbatim}
%\begin{lstlisting}[language=C++]

\begin{lstlisting}[language=C++]
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What are the contents of the array after the following statements? 
int bar[6] = {6, 5, 3, 8, 1, 9}; 
int temp; 
temp = bar[4]; 
bar[4] = bar[1]; 
bar[1] = temp; 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What are the contents of the array after the following?
int documents[6] = {3, 3, 10, 1, 1, 2};
for (int i = 0; i < 6; i += 1)
{ 
	documents[i] += 5; 
} 
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
What is printed after the following statements?
int dogs[6] = {0, 1, 7, 3, 0, 2}; 
for (int i = 1; i < 4; i = i + 1) 
{ 
	cout << dogs[i] << " ";
} 
\end{lstlisting}

@@

The unique answer guarantee used here is also the same as Difficulty 1, but more constraints must be put in place. Because the array elements are not guaranteed to be unique, then the
elements of the vector are also not guaranteed to be unique. Then there may be a case where the number of the permutations of the vector is not great enough that we can simply shuffle 
the answer. Take S to be the set of unique values in the correct answer. Then the factorial of the length of the vector divided by the product of the factorial of the occurence of each element S 
in the original vector (i.e. the number of permutations) must be greater than or equal to 5 (the total number of answers). Here is a direct example:

IS THIS WORTH EXPLAINING? IS THIS TOO DIFFICULT? DOES ANYONE CARE
also change format if keeping

Correct = \{1, 1, 1, 2\}; \par
S = \{1, 2\}; \par
Number of instances of each s in S in Correct: \par
1 : 3 \par
2 : 1 \par
Product of these factorials = factorial(3) * factorial(1) = 6\par
Total Permutations of Correct = factorial(length of Correct) / Product = factorial(4) / 6 = 4 \par

@@

The objective of this first question is to simply test return types and any type coercion that takes place. It features a function with no parameters and a single return statement with a simple arithmetic statement. In the return expression, two float operands are used (any value between 1 and 10 in steps of 0.5) with a single operation (any of +, -, *, or /). There may be an opportunity here to randomize the amount of operands in the expression, but as it's not essential to the question, we have not considered it. Here is an example:

\begin{lstlisting}[language=C++]
Given the following function definition:
int Pow() 
{ 
	return 4.5 + 1.0; 
} 
What is printed from the following call? 
cout << Pow() << endl; 
\end{lstlisting}

In addition to the randomness described above, the essential random element is the return type of the function. Of course, a different return type will produce different answers for the same return expression, so this provides the main random element. The return type can be any of (TODO make different font?) Int, Float, or Void. In the case that the return type is Void, the correct
answer is actually a "Compile-time error", similar to some difficulties in Loop Printing.

@@

\begin{lstlisting}[language=C++]
Given the following function definition:
float Switch(float a, int b)
{
    return a - b;
}
What is printed from the following call?
cout << Switch(3.5, 1.5) << endl;
\end{lstlisting}

@@

\begin{lstlisting}[language=C++]
Given the following function definition:
void Calculate(int& a, int& b, int c)
{
	b = a / b + c;
}

>>>>

\usepackage{amsmath}

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, language=C++}

\usepackage{fancyvrb}
\DefineVerbatimEnvironment{VerbCM}{Verbatim}{fontfamily=cm} %default latex typeface

@@

\begin{Verbatim}[tabsize=4]
::Dynamic Expressions Level 1 #005::
What is the variable "size" equal to?
<pre> int item = 4; 
int size = item / 3 - 3;</pre>
	{ 
	=-2 
	~-0.5 
	~-1.667 
	~1.5 
	~0 
	}
\end{Verbatim}

@@

One of the most interesting aspect of this system, and one of its main goals, is to produce convincing distractors -- that is, wrong answers offerred as an option to the student. Distractors
are essential to all multiple choice questions, because any options that students can easily identify as wrong take away from the difficulty of a question, and ultimately, does not add to the measure of knowledge of a student. Any blatant distractors make it easier for students to select (or guess) the correct answer.

This notion is also present in other systems (reference for nlp questions), but with varying success. This implementation is novel for similar systems based on deterministic methods (reference). Between categories, and sometimes between difficulties, there are different methods for generating distractors, specific to each question. We discuss all of the methods below within each category, but here is an examples in GIFT.

\begin{Verbatim}
What is the variable "bar" equal to?
int foo = 2;
int bar = foo - 4 / 3 + 4;
{
	=5
	~4
	~4.67
	~2
	~3.33
}
\end{Verbatim}

The first distractor method disregards the order of operations and simply evaluates the expression from left to right. The next method uses float operands and operations (a common mistake for beginners), and the third method evaluates the expression from right to left. The fourth and final method combines the first two, by disregarding the order of operations and using float operands and operations.

While our main goal is to have every distractor be, not only plausible, but convincing, it becomes difficult when very general methods are used, as it can be the case that the same answer occurs twice. We will now discuss how to prevent duplicates and guarantee that all answers are unique.

@@

Because of the universal format for questions, extra error checks can be done across all categories. While there is no general way
to ensure that each question provides the correct answer (other than unit testing), we can confirm that each answer is unique and, especially, that no distractor is the same as the right answer -- a seemingly trivial, but essential, restraint. If there are repeating answers, then either the right answer is repeated as a wrong answer (in which case, a student may be penalized for picking the right answer), or a wrong answer is repeated twice (most students will disregard this answer as false). Both of these situations results in an unusable question, and this is unacceptable.

Producing unique answers can become complicated is for two reasons: i) each category generates its own distractors using "clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes) and ii) complex answers
(in particular, answers containing vectors; see Arrays) become more difficult to compare and even more difficult
to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
In the case of (i), it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of (ii), if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see Arrays
Difficulty 1). It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

@@

While this is not a main focus of this paper, it should be noted that there are measures taken within each question to prevent trivial cases. For example, simple expressions such as \verb;1 * x - x; or a loop body that never executes (in the context of counting the number of iterations) are far too simple to test student knowledge, and this takes away from the objective of the question. We are able to set parameters when generating the questions that will hopefully restrict their occurrence, yet, due to the random nature of the questions, trivial questions may still appear. As a response, this system checks for predetermined, common trivial cases (such as a loop that iterates not enough) are changed to try and provide a more difficult question.

@@

\begin{lstlisting}
int documents = 8;
int bar = 10;
(bar < = documents) != (10 < 9)
\end{lstlisting}

@@

\begin{lstlisting}
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}

@@

\begin{lstlisting}
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}

@@

\begin{lstlisting}
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}

@@

\begin{lstlisting}
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}

@@

\begin{lstlisting}
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}

@@

\begin{lstlisting}
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}

@@

\begin{lstlisting}
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}

@@

\begin{lstlisting}
What are the contents of the array after the following statements? 
int bar[6] = {6, 5, 3, 8, 1, 9}; 
int temp; 
temp = bar[4]; 
bar[4] = bar[1]; 
bar[1] = temp; 
\end{lstlisting}

@@

\begin{lstlisting}
What are the contents of the array after the following?
int documents[6] = {3, 3, 10, 1, 1, 2};
for (int i = 0; i < 6; i += 1)
{ 
	documents[i] += 5; 
} 
\end{lstlisting}

@@

\begin{lstlisting}
What is printed after the following statements?
int dogs[6] = {0, 1, 7, 3, 0, 2}; 
for (int i = 1; i < 4; i = i + 1) 
{ 
	cout << dogs[i] << " ";
} 
\end{lstlisting}

@@

The unique answer guarantee used here is also the same as Difficulty 1, but more constraints must be put in place. Because the array elements are not guaranteed to be unique, then the
elements of the correct answer vector are also not guaranteed to be unique. Then there may be a case where the number of the permutations of this vector is not great enough that we can simply shuffle 
the answer. Take $ U $ to be the set of unique values in the correct answer (a vector called $ C $). We then construct another vector, say $ V $, that, for each element in $ U $, counts the number of occurences in $ C $.  Then the factorial of the length of $ C $ divided by the product of the factorial of each element in $ V $ 
 (i.e. the number of permutations) must be greater than or equal to 5 (the total number of answers).

\begin{equation*}
V = \textrm{Number of occurrences in } C\! \forall\! u \in U
\end{equation*}

\begin{equation*}
\textrm{Number of permutations} = \frac{length(C)!}{\displaystyle \prod_{v \in V} v!}
\end{equation*}

\noindent Here is a direct example:

\begin{Verbatim}
C = {1, 1, 1, 2};
S = {1, 2}; 
V = {3, 1};
\end{Verbatim}
\begin{equation*}
\textrm{Number of permutations} = \frac{length(C)!}{\displaystyle \prod_{v \in V} v!} = \frac{24}{6} = 4
\end{equation*}

@@

The objective of this first question is to simply test return types and any type coercion that takes place. It features a function with no parameters and a single return statement with a simple arithmetic statement. In the return expression, two float operands are used (any value between 1 and 10 in steps of 0.5) with a single operation (any of +, -, *, or /). In the future, there may be an opportunity here to randomize the amount of operands in the expression, but as it's not essential to the question, we have not yet considered it. Here is an example:

\begin{VerbCM}
Given the following function definition:
\end{VerbCM}
\begin{lstlisting}
int Pow() 
{ 
	return 4.5 + 1.0; 
}
\end{lstlisting}
\begin{VerbCM}
What is printed from the following call? 
\end{VerbCM}
\begin{lstlisting}
cout << Pow() << endl; 
\end{lstlisting}

In addition to the randomness described above, the essential random element is the return type of the function. Of course, a different return type will produce different answers for the same return expression, so this provides the main random element. The return type can be any of  \texttt{int}, \texttt{float}, or \texttt{void}. In the case that the return type is Void, the correct
answer is actually a "Compile-time error", similar to some difficulties in Loop Printing.

@@

\begin{VerbCM}
Given the following function definition:
\end{VerbCM}
\begin{lstlisting}
float Switch(float a, int b)
{
    return a - b;
}
What is printed from the following call?
cout << Switch(3.5, 1.5) << endl;
\end{lstlisting}

@@

\begin{lstlisting}
Given the following function definition:
void Calculate(int& a, int& b, int c)
{
	b = a / b + c;
}
